\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}

At the end of this project, we have successfully delivered a complete Credix digital payment management platform, designed and developed using Agile Scrum methodology. The platform leverages a modern client-server architecture with Flutter for the mobile frontend and Spring Boot for the backend REST APIs, ensuring scalability, maintainability, and a clear separation of concerns.\par

From the initial sprints, we established the foundational components: secure JWT-based authentication, fine-grained role management (Super Admin, Admin, End User), and a robust credit management system for inter-company transactions. The Flutter frontend follows Clean Architecture principles with a five-layer structure (Presentation, State Management with BLoC, Domain, Data, and Core layers), while the Spring Boot backend implements a three-tier architecture (Controllers, Business Services, and Data Access with JPA Repositories) backed by PostgreSQL for data persistence.\par

Throughout subsequent sprints, we enriched the platform with advanced features including a hierarchical credit distribution system where Super Admins distribute bulk credit to Admins after cash payment verification at ASM, automated credit allocation from Admins to end users, real-time transaction monitoring, and comprehensive analytics dashboards providing complete visibility on payment flows and expenses. Integration with ASM POS APIs enables seamless barcode scanning and payment validation, ensuring smooth real-time operations.\par

The entire system was industrialized through automated CI/CD pipelines orchestrated by Jenkins. GitHub webhooks trigger Jenkins builds upon code commits, which compile the applications, run automated tests, build Docker images for the backend, generate APK and AAB files for the Flutter mobile app, and deploy the backend to Render's cloud infrastructure. Build artifacts are systematically stored in Google Drive for version tracking and audit purposes. This automation ensures rapid, reliable, and consistent delivery of updates while minimizing manual deployment errors.\par

For the future, several promising avenues exist to further enhance Credix: expanding payment method options beyond the current system, enriching predictive analytics capabilities with machine learning models for fraud detection and spending pattern analysis, implementing real-time notifications for critical events, and extending the platform to serve additional business sectors beyond the current scope. These enhancements will transform Credix into an increasingly intelligent and versatile solution centered on evolving business needs.
