\chapter*{Acknowledgments}
\justifying
\sloppy

First and foremost, I would like to express my gratitude and appreciation to all those  
who have provided their support for the realization of this project.

\vspace{0.5cm}

I would particularly like to thank my family, whose moral support, patience and  
constant encouragement have been an invaluable source of motivation. Their presence by  
my side has enabled me to overcome challenges and give my best in this  
project.

\vspace{0.5cm}

I wish to express my profound gratitude to my academic supervisor, Mr. \textbf{Fahmi KALLEL},  
for his availability, rigor and pertinent advice throughout this work.  
His guidance has greatly contributed to the successful completion of this project.

\vspace{0.5cm}

I would like to extend my sincere thanks to my technical supervisor, Mr. \textbf{Youssef AOUADNI},  
for his technical leadership, expertise and valuable guidance throughout the development process.  
His insights and support have been instrumental in bringing this project to fruition.

\vspace{0.5cm}

I would also like to express my deep gratitude to the entire teaching and administrative staff of the International Institute of Technology (IIT), for the quality of education provided, their professionalism and constant commitment to offering students updated training that meets market requirements. I thank the administration, academic coordinators and all IIT staff for their support throughout my academic journey and for establishing favorable conditions for learning and success.
