\section{Functional Requirements}

Functional requirements describe the set of services and interactions that the system must provide to satisfy the users of Credix. They are organized according to the sprint-based development approach, covering core payment functionality, credit management capabilities, analytics and reporting features, and system administration.

\subsection{User and Account Management (Sprint 1)}
\begin{itemize}
    \item Creation, modification, and logical deletion of accounts (SUPER\_ADMIN, ADMIN, USER).
    \item Secure authentication (email/password, JWT, token refresh).
    \item Management of roles and permissions according to user type.
    \item Hierarchical account management (SUPER\_ADMIN manages ADMINs, ADMINs manage USERs).
    \item User account management within the organizational structure (addition, removal, status tracking).
\end{itemize}

\subsection{Core Payment Processing (Sprint 2)}
\begin{itemize}
    \item Generation of unique, time-bound (e.g., 30-second expiry) 1D barcodes (e.g., Code128 format) linked to the user's tokenized wallet ID.
    \item Real-time validation of barcode payments by the Spring Boot backend upon scanning.
    \item Processing of payment transactions, including debiting the user's wallet and crediting the merchant's account.
    \item Display of current digital wallet balance for users with real-time updates.
\end{itemize}

\subsection{Credit Management (Sprint 3)}
\begin{itemize}
    \item \textbf{Hierarchical Credit Distribution}: SUPER\_ADMIN distributes credit to ADMIN users after Admin provides cash payment at ASM, based on predefined wallet transfer amounts.
    \item \textbf{Credit Allocation}: ADMIN users can allocate and de-allocate credit to individual USER accounts with customizable spending limits.
    \item \textbf{Transaction Monitoring}: Real-time tracking of user transactions, credit consumption, and remaining balances across the hierarchy.
    \item Management of credit pools at each level, including top-up functionalities and balance tracking.
    \item Enforcement of spending policies and limits at both ADMIN and USER levels.
    \item Notifications for credit allocation, depletion alerts, and policy violations.
\end{itemize}

\subsection{Analytics and Reporting (Sprint 4)}
\begin{itemize}
    \item \textbf{Spending Analytics}: Interactive dashboards displaying credit consumption trends, user spending patterns, and transaction analysis.
    \item \textbf{Financial Reports}: Generation of comprehensive financial reports (credit allocation, usage summaries, transaction details) in PDF/CSV formats.
    \item Graphical visualization of key metrics with dynamic filtering capabilities (period, user, transaction type).
    \item Real-time analytics updates with drill-down capabilities for detailed transaction analysis.
    \item Automated report scheduling and delivery to administrators.
    \item Comparative analytics across different time periods and user groups.
\end{itemize}

\subsection{System Administration and Security}
\begin{itemize}
    \item Administrator dashboard for real-time system monitoring, user activity logs, and transaction oversight.
    \item System alerts for errors or critical events.
    \item Secure tokenization of wallet IDs and sensitive data encryption.
    \item Multi-language support for notifications and interfaces (English, French, Arabic).
    \item Transaction history and settlement tracking for all user levels.
    \item Customizable notification preferences for all user types.
\end{itemize}
