\section{Non-functional Requirements}

Non-functional requirements define the quality, performance, and security constraints of the system. They ensure the robustness, efficiency, and usability of Credix.

\subsection{Security}
\begin{itemize}
    \item Encryption of sensitive data (JWT tokens, end user credentials, transaction details, and any stored media).
    \item Protection against common web vulnerabilities (e.g., Cross-Site Scripting (XSS), Cross-Site Request Forgery (CSRF), SQL injection).
    \item Implementation of comprehensive security logs and a robust logging system for critical actions and system events.
    \item Secure API endpoints with proper authentication and authorization mechanisms.
    \item Data anonymization or pseudonymization for sensitive end user information where applicable.
\end{itemize}

\subsection{Performance}
\begin{itemize}
    \item Ensure fast API response times for end user requests, especially critical for real-time payment validation during peak usage periods.
    \item The system must be capable of handling a high volume of concurrent transactions to accommodate transaction volume.
    \item Optimize database queries and backend processes to ensure efficient data retrieval and processing.
    \item Design the system architecture to maintain performance under increasing load.
\end{itemize}

\subsection{Maintainability and Testing}
\begin{itemize}
    \item Code structured into well-defined modules (front-end, back-end, shared services, API integration layer) to facilitate understanding and future modifications.
    \item Achieve comprehensive unit test coverage for critical business logic and core functionalities.
    \item Provide comprehensive API documentation (e.g., using Swagger/OpenAPI) and detailed deployment guides to ensure ease of maintenance and onboarding for new developers.
    \item Implement automated integration and end-to-end tests to ensure the seamless interaction between different system components.
\end{itemize}

\subsection{Usability (UX/UI)}
\begin{itemize}
    \item Develop a clear, accessible, and responsive interface that adapts seamlessly across various devices and screen sizes.
    \item Adhere to established ergonomic standards, ensuring intuitive navigation, minimal cognitive load, and a consistent end user experience across all modules.
    \item Utilize a modern and professional design aesthetic, with fluid transitions and interactions between different application sections, enhancing end user satisfaction for all user roles.
    \item Provide clear feedback mechanisms for end user actions, such as payment confirmations and error messages.
\end{itemize}
