\section{Proposed Solution}

\subsection{General presentation of the solution}

To address the identified needs and overcome the shortcomings of existing applications, we propose \textbf{Credix}, a comprehensive, modular, and scalable web-based application. It centralizes the management of digital meal vouchers, secure payments, admin credit distribution, and real-time transaction tracking within a secure and ergonomic interface. Designed with Angular for the front-end and Spring Boot for the back-end, Credix relies on a robust, continuously deployed architecture via CI/CD pipelines, ensuring rapid updates, reliability, and accessibility from any device.

\subsection{Key Solution Functions}

Credix offers a suite of functionalities designed to streamline credit management, secure payment processing, and organizational oversight:

\begin{itemize}
    \item \textbf{Secure Wallet Management and Authentication:}
    Each user is assigned a digital wallet upon account creation, identified by a unique tokenized ID. The wallet stores the user's credit balance and transaction history. Authentication is handled through secure email/password credentials with JWT token-based session management, ensuring that only authorized users can access their wallets and perform transactions.

    \item \textbf{Barcode Payment and Real-time Validation:}
    Users can initiate payments by generating a unique, time-bound 1D barcode (Code128 format) directly from their wallet interface. Each barcode has a 30-second validity window to prevent unauthorized reuse or interception. Upon scanning, the Spring Boot backend validates the barcode in real-time, verifies the user's wallet balance, processes the transaction by debiting the user's wallet and crediting the merchant's account, and returns an immediate confirmation or error message.

    \item \textbf{Hierarchical Credit Management:}
    Credix implements a three-tier role-based system (SUPER\_ADMIN, ADMIN, USER) enabling efficient credit distribution across organizational hierarchies. SUPER\_ADMIN users can purchase and distribute bulk credit to ADMIN users, who in turn allocate credit to end-USER accounts. Each wallet can be configured with specific transfer amounts, allowing precise control over credit allocation limits. The system supports bulk credit transfer operations, enabling administrators to distribute credits to multiple users simultaneously based on predefined wallet transfer amounts, significantly reducing manual effort and ensuring consistent allocation.

    \item \textbf{Comprehensive Dashboards and Reporting:}
    Administrators have access to real-time dashboards displaying credit consumption trends, user spending patterns, and transaction summaries. The system generates detailed financial reports in PDF and CSV formats, including credit allocation histories, usage summaries, and transaction details. Visual graphs and charts provide insights into spending behavior, with dynamic filtering capabilities by period, user, and transaction type. Users can view their personal transaction history and current wallet balance through intuitive interfaces.

    \item \textbf{Admin and User Portals:}
    The platform provides role-specific web interfaces tailored to each user type. SUPER\_ADMIN and ADMIN users access comprehensive management dashboards for user account creation, wallet management, bulk credit distribution, and system monitoring. End-USER accounts access simplified interfaces displaying wallet balance, transaction history, barcode generation for payments, and profile management. All interfaces are designed with responsive layouts ensuring optimal user experience across desktop and mobile devices.

    \item \textbf{Robust Security Architecture:}
    The system implements JWT-based authentication with secure token refresh mechanisms, ensuring session security without compromising user experience. All sensitive data, including wallet IDs and transaction details, are encrypted both in transit and at rest. The platform enforces role-based access control (RBAC), ensuring users can only access functionalities appropriate to their permission level. Transaction logs are maintained for audit purposes, providing complete traceability of all credit movements and system operations.
\end{itemize}

\begin{table}[!htbp]
    \caption{Key Innovations of Credix Compared to Existing Solutions} 
    \centering
    \renewcommand{\arraystretch}{1.5}
    \label{tab:innovations_credix}
    \begin{tabularx}{\textwidth}{|X|X|X|}
        \hline
        \textbf{Functionality} & \textbf{Existing Solutions} & \textbf{Credix (Our Project)} \\ 
        \hline
        Hierarchical Credit Distribution
        & \textcolor{orange}{\ding{70}} Limited hierarchy support
        & \textcolor{green}{\ding{51}} Three-tier role-based distribution system \\
        \hline
        Time-Bound Barcode Payments
        & \textcolor{red}{\ding{55}} Static QR codes or no barcode support
        & \textcolor{green}{\ding{51}} 30-second validity window with Code128 format \\
        \hline
        Web-Based Administration
        & \textcolor{orange}{\ding{70}} Desktop applications required
        & \textcolor{green}{\ding{51}} Modern Angular interface accessible anywhere \\
        \hline
        Bulk Credit Transfer Operations
        & \textcolor{red}{\ding{55}} Manual individual transfers
        & \textcolor{green}{\ding{51}} Automated bulk transfers with predefined amounts \\
        \hline
        Real-time Transaction Processing
        & \textcolor{orange}{\ding{70}} Delayed batch processing
        & \textcolor{green}{\ding{51}} Instant validation and wallet updates \\
        \hline
        Configurable Wallet Transfer Limits
        & \textcolor{orange}{\ding{70}} Fixed allocation rules
        & \textcolor{green}{\ding{51}} Flexible per-wallet transfer amount configuration \\
        \hline
        Role-Based Access Control
        & \textcolor{orange}{\ding{70}} Basic user permissions
        & \textcolor{green}{\ding{51}} Comprehensive three-tier permission system \\
        \hline
        Scalable Architecture
        & \textcolor{orange}{\ding{70}} Monolithic systems
        & \textcolor{green}{\ding{51}} Spring Boot microservices with PostgreSQL \\
        \hline
    \end{tabularx}
\end{table}

The entirety of these functionalities, supported by a robust technical architecture and an automated DevOps process, offers a coherent, secure, and perfectly adapted user experience to the expectations of organizations in the digital meal voucher ecosystem.
